Title goes here.

### 2018-12-20 analysis/poisson.Rmd
Misc. revisions to READMEs and documentation.

```{r spikes-violin-plots, fig.height=5, fig.width=7}
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
					                 mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
p <- ggplot(pdat1,aes(x = method,y = mise,fill = method.type)) +
     geom_violin(fill = "skyblue",color = "skyblue") +
     geom_boxplot(width = 0.15,outlier.shape = NA) +
     scale_y_continuous(breaks = seq(6,16,2)) +
     scale_fill_manual(values = c("darkorange","dodgerblue","gold"),
                       guide = FALSE) +
     coord_flip() +
     labs(x = "",y = "MISE") +
     theme(axis.line = element_blank(),
           axis.ticks.y = element_blank())
```

>>>>

```{r spikes-violin-plots, fig.height=5, fig.width=7}
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
					                 mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
n     <- length(mise.ash.s.1)
pdat1 <- data.frame(method = rep(c("SMASH","BMSM","HF"),each = n),
 				    mise   = c(mise.ash.s.1,mise.BMSM.s.1,mise.hf.ti.r.s.1))
p1    <- 
vioplot.col(mise.ash.s.1, mise.BMSM.s.1, mise.hf.ti.r.s.1, horizontal = TRUE,
  names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)
abline(v = median(mise.ash.s.1), lty = 3, col = 3)

p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
      coord_flip()
      labs(x = "",y = "MISE") +
     theme(axis.line = element_blank(),
           axis.ticks.y = element_blank())
```
